Meta-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates

### 2025-02-13 paper/1_Initial/manuscript.qmd
works

---
title: "Meta-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates"
shorttitle: "IAS Meta-analysis"
author:
  - name: Ana Neves
    orcid: 0009-0006-0020-7599
    roles:
      - Project administration
      - Data curation
      - Formal Analysis
      - Investigation
      - Visualization
      - Writing – original draft
      - Writing – review & editing
    affiliations:
      - id: "id1"
        name: "University of Sussex"
        department: "School of Psychology"
        city: "Brighton"
        country: "UK"
        postal-code: "BN1 9RH"
# author-note:
#   status-changes: 
#     affiliation-change: null
#     deceased: null
#   disclosures:
#     study-registration: null
#     data-sharing: null
#     related-report: null
#     conflict-of-interest: null
#     financial-support: null
#     gratitude: null
#     authorship-agreements: null
    #   # - Project administration
    #   # - Data curation
    #   # - Formal Analysis
    #   # - Investigation
    #   # - Visualization
    #   # - Writing – original draft
    #   # - Writing – review & editing
    # Roles are optional. 
    # conceptualization, data curation, formal Analysis, funding acquisition, investigation, 
    # methodology, project administration, resources, software, supervision, validation, 
    # visualization, writing, editing
    #   - Conceptualization
    #   - Data curation
    #   - formal Analysis
    #   - Funding acquisition
    #   - Investigation
    #   - Methodology
    #   - Project administration
    #   - Resources
    #   - Software
    #   - Supervision
    #   - Validation
    #   - Visualization
    #   - Writing – original draft
  #   #   - Writing – review & editing
  # - name: Magdalena Pfaff
  #   orcid: 0009-0006-2386-7936
  #   affiliations:
  #     - ref: "id1" 
  # - name: Dominique Makowski
  #   corresponding: true
  #   orcid: 0000-0001-5375-9967
  #   email: D.Makowski@sussex.ac.uk
  #   url: https://realitybending.github.io/
  #   roles:
  #     - Conceptualization
  #     - Data curation
  #     - Formal Analysis
  #     - Funding acquisition
  #     - Investigation
  #     - Methodology
  #     - Project administration
  #     - Resources
  #     - Software
  #     - Supervision
  #     - Validation
  #     - Visualization
  #     - Writing – original draft
  #   affiliations:
  #     - ref: "id1"
  #     - name: "University of Sussex"
  #       department:  "Sussex Centre for Consciousness Science"
author-note:
  disclosures:
    gratitude: |
      ::: {.callout-note icon=false appearance="simple"}
      :::
      This preprint is a non-peer-reviewed work from the [**Reality Bending Lab**](https://realitybending.github.io/).
      ![](https://realitybending.github.io/media/ReBeL_LogoOnly_hu11484441381606756729.png){width=20% fig-align="center"}
abstract: |
  Blabla the abstract blabla.
keywords: [keyword1, keyword2, keyword3]
floatsintext: true
numbered-lines: true
bibliography: bibliography.bib
suppress-title-page: false
mask: false
# Language options. See https://quarto.org/docs/authoring/language.html
lang: en
language:
  citation-last-author-separator: "and"
  citation-masked-author: "Masked Citation"
  citation-masked-date: "n.d."
  citation-masked-title: "Masked Title"
  title-block-author-note: "Author Note"
  title-block-correspondence-note: "Correspondence concerning this article should be addressed to"
  title-block-role-introduction: "Author roles were classified using the Contributor Role Taxonomy (CRediT; https://credit.niso.org/) as follows:"
  references-meta-analysis:
format:
  apaquarto-pdf:
    # Can be jou (journal), man (manuscript), stu (student), or doc (document)
    documentmode: man
    include-in-header:
      - text: |
          \usepackage{lscape}
  apaquarto-docx: default
  apaquarto-html: default
editor: 
  markdown: 
    wrap: sentence
editor_options: 
  chunk_output_type: console
---

@@

```{r}
#| warning: false 
#| label: "fig-measures"
#| fig-cap: "Different ways in which interoception can be measured."
#| apa-twocolumn: true  # A Figure Spanning Two Columns When in Journal Mode
## | out-width: "100%"

@@

Our search focused on studies citing the original IAS validation paper [@murphy2019], identifying 136 papers (as of 01/05/2024).
To qualify for inclusion, papers needed to (1) provide accessible data in open-access, (2) employ the IAS as a measure, and (3) report individual IAS items scores.
A total of 10 studies was included (see **Table 1**).
We also included the data of two unpublished (but already open-access) studies from the authors and one from another researcher.
The total N participants was 32,214 participants (*Mean* = 48.6 years, *SD* = 13.1, 71.6% Female).

@@

To examine the factor structure of the IAS, a two-step approach was employed.
First, Exploratory Graph Analysis (EGA), was used to estimate the dimensions via network estimation and community detection, alongside assessing the stability of dimensions and items using the bootstrapping techniques [@golino2017exploratory].
The selection of EGA was motivated by its capability to handle complex, multidimensional data and provide robust dimension estimates.
A novel network psychometrics - Unique variable analysis [UVA, @christensen2023unique] - approach based on the weighted topological overlap will be computed to evaluate which items have substantial local dependence (\> 0.25).
Subsequently, exploratory factor analysis (EFA) was employed followed by confirmatory factor analysis (CFA).

>>>>

---
title: "Meta-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates"
shorttitle: "IAS Meta-analysis"
author:
  - name: Ana Neves
    orcid: 0009-0006-0020-7599
    roles:
      - Project administration
      - Data curation
      - Formal Analysis
      - Investigation
      - Visualization
      - Writing – original draft
      - Writing – review & editing
    affiliations:
      - id: "id1"
        name: "University of Sussex"
        department: "School of Psychology"
        city: "Brighton"
        country: "UK"
        postal-code: "BN1 9RH"
# author-note:
#   status-changes: 
#     affiliation-change: null
#     deceased: null
#   disclosures:
#     study-registration: null
#     data-sharing: null
#     related-report: null
#     conflict-of-interest: null
#     financial-support: null
#     gratitude: null
#     authorship-agreements: null
    #   # - Project administration
    #   # - Data curation
    #   # - Formal Analysis
    #   # - Investigation
    #   # - Visualization
    #   # - Writing – original draft
    #   # - Writing – review & editing
    # Roles are optional. 
    # conceptualization, data curation, formal Analysis, funding acquisition, investigation, 
    # methodology, project administration, resources, software, supervision, validation, 
    # visualization, writing, editing
    #   - Conceptualization
    #   - Data curation
    #   - formal Analysis
    #   - Funding acquisition
    #   - Investigation
    #   - Methodology
    #   - Project administration
    #   - Resources
    #   - Software
    #   - Supervision
    #   - Validation
    #   - Visualization
    #   - Writing – original draft
  #   #   - Writing – review & editing
  # - name: Magdalena Pfaff
  #   orcid: 0009-0006-2386-7936
  #   affiliations:
  #     - ref: "id1" 
  # - name: Dominique Makowski
  #   corresponding: true
  #   orcid: 0000-0001-5375-9967
  #   email: D.Makowski@sussex.ac.uk
  #   url: https://realitybending.github.io/
  #   roles:
  #     - Conceptualization
  #     - Data curation
  #     - Formal Analysis
  #     - Funding acquisition
  #     - Investigation
  #     - Methodology
  #     - Project administration
  #     - Resources
  #     - Software
  #     - Supervision
  #     - Validation
  #     - Visualization
  #     - Writing – original draft
  #   affiliations:
  #     - ref: "id1"
  #     - name: "University of Sussex"
  #       department:  "Sussex Centre for Consciousness Science"
author-note:
  disclosures:
    gratitude: |
      ::: {.callout-note icon=false appearance="simple"}
      This preprint is a non-peer-reviewed work from the [**Reality Bending Lab**](https://realitybending.github.io/).
      ![](https://realitybending.github.io/media/ReBeL_LogoOnly_hu11484441381606756729.png){width=20% fig-align="center"}
      :::
abstract: |
  Blabla the abstract blabla.
keywords: [keyword1, keyword2, keyword3]
floatsintext: true
numbered-lines: true
bibliography: bibliography.bib
suppress-title-page: false
mask: false
# Language options. See https://quarto.org/docs/authoring/language.html
lang: en
language:
  citation-last-author-separator: "and"
  citation-masked-author: "Masked Citation"
  citation-masked-date: "n.d."
  citation-masked-title: "Masked Title"
  title-block-author-note: "Author Note"
  title-block-correspondence-note: "Correspondence concerning this article should be addressed to"
  title-block-role-introduction: "Author roles were classified using the Contributor Role Taxonomy (CRediT; https://credit.niso.org/) as follows:"
  references-meta-analysis:
format:
  apaquarto-pdf:
    # Can be jou (journal), man (manuscript), stu (student), or doc (document)
    documentmode: man
    include-in-header:
      - text: |
          \usepackage{lscape}
  apaquarto-docx: default
  apaquarto-html: default
editor: 
  markdown: 
    wrap: sentence
editor_options: 
  chunk_output_type: console
---

@@

```{r}
#| warning: false 
#| label: "fig-measures"
#| fig-cap: "Different ways in which interoception can be measured."
#| apa-twocolumn: false  # A Figure Spanning Two Columns When in Journal Mode
#| out-width: "100%"

@@

Our search focused on studies citing the original IAS validation paper [@murphy2019], identifying 136 papers (as of 01/05/2024).
To qualify for inclusion, papers needed to (1) provide accessible data in open-access, (2) employ the IAS as a measure, and (3) report individual IAS items scores.
We also included the data of two unpublished (but already open-access) studies.
A total of 10 studies was included (see **Table 1**).

The total number of participants was 32,214 participants (Mean = 48.6 $\pm$ 13.1, 71.6\% Female).

@@

To examine the factor structure of the IAS, a two-steps approach was employed.
First, Exploratory Graph Analysis (EGA), was used to estimate the dimensions via network estimation and community detection, alongside assessing the stability of dimensions and items using the bootstrapping techniques [@golino2017exploratory].
The selection of EGA was motivated by its capability to handle complex, multidimensional data and provide robust dimension estimates.
A novel network psychometrics - Unique variable analysis [UVA, @christensen2023unique] - approach based on the weighted topological overlap will be computed to evaluate which items have substantial local dependence (\> 0.25).
Subsequently, exploratory factor analysis (EFA) was employed followed by confirmatory factor analysis (CFA).
